Manuscript

### 2023-05-24 Manuscript1.Rmd
updates

#ratings
df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
#cue-contingency
df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()

@@

rw_fit_sess1$diagnostic_summary()
```

@@

rw_fit_sess2$diagnostic_summary()

@@

mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))

@@

diag_sigmaEta = get_diag(fit = kalman_fit_sess1,
         parameter = "sigmaEta")

diag_sigmaPsi = get_diag(fit = kalman_fit_sess1,
         parameter = "sigmaPsi")

diag_sigmaEpsilon = get_diag(fit = kalman_fit_sess1,
         parameter = "sigmaEpsilon")

diag_sigmabeta = get_diag(fit = kalman_fit_sess1,
         parameter = "beta")

diag_precision_percept = get_diag(fit = kalman_fit_sess1,
         parameter = "precision_percept")
```

@@

mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))

@@

wb_fit_sess1  <- mod$sample(
      data = data1,
      chains = 4, 
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )
```

@@

w7b_fit_sess2 <- mod$sample(
      data = data1,
      chains = 4, 
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )

>>>>

@@

ppu_hier(fit = rw_fit_sess1,
         parameters = c("alpha","w1","precision_percept"),
         reals = NA)

```{r plotting 1 agent}

percept = sum %>% filter(str_detect(variable, "painMu"))
percept = percept[1:160,]

expect = sum %>% filter(str_detect(variable, "expectMu"))
expect = expect[1:160,]

percept$stim = data$stim
percept$expect = expect$mean

percept %>% ggplot(aes(x=1:nrow(.), y = mean, col = as.factor(stim)))+geom_point()

percept %>% ggplot(aes(x=expect, y = mean, col = as.factor(stim)))+geom_point()

ass = sum %>% filter(str_detect(variable, "associ"))
ass = ass[1:161,]

ass %>% ggplot(aes(x=1:nrow(.), y = mean))+geom_line()+geom_point(data = data, aes(x = trial, y = u))

rw_fit_sess1$diagnostic_summary()

alpha = get_diag(rw_fit_sess1, "alpha")
w1 = get_diag(rw_fit_sess1, "w1")
pp = get_diag(rw_fit_sess1, "precision_percept")
beta = get_diag(rw_fit_sess1, "beta")

@@

ppu_hier(fit = rw_fit_sess2,
         parameters = c("alpha","w1","precision_percept"),
         reals = NA)

@@

mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))

@@

ppu_hier(fit = kalman_fit_sess1,
         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
         reals = NA)

# 
# ppu_sub(fit = fit,
#         parameter = "precision_percept",
#         reals = df,
#         lims = -1,
#         lime = 10,
#         nsubs = NA
#         )

get_diag(kalman_fit_sess1, "sigmaEta")
get_diag(kalman_fit_sess1, "sigmaPsi")
get_diag(kalman_fit_sess1, "sigmaEpsilon")

sum = kalman_fit_sess1$summary()

ass = sum %>% filter(str_detect(variable, "perceptmuu"))
ass = ass[(161*2-1):(161*3-1),]

exp = sum %>% filter(str_detect(variable, "exp_muu"))
exp = exp[(161*2-1):(161*3-1),]

ass$exp = exp$mean

ass %>% ggplot(aes(x=exp, y = mean))+geom_point()

@@

mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2_nocent.stan"))

@@

wb_fit_sess1  <- mod$sample(
      data = data1,
      chains = 4, 
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )

wb_fit_sess1$diagnostic_summary()

alpha = get_diag(wb_fit_sess1, "alpha")
w1 = get_diag(wb_fit_sess1, "w1")
w2 = get_diag(wb_fit_sess1, "w2")
pp = get_diag(wb_fit_sess1, "percept_precision")
beta = get_diag(wb_fit_sess1, "beta")

@@

wb_fit_sess2 <- mod$sample(
      data = data1,
      chains = 4, 
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )

alpha = get_diag(wb_fit_sess1, "alpha")
w1 = get_diag(wb_fit_sess1, "w1")
w2 = get_diag(wb_fit_sess1, "w2")
pp = get_diag(wb_fit_sess1, "percept_precision")
beta = get_diag(wb_fit_sess1, "beta")

```{r}
get_corplot(rw_fit_sess1, rw_fit_sess2, "alpha")
get_corplot(rw_fit_sess1, rw_fit_sess2, "w1")
get_corplot(rw_fit_sess1, rw_fit_sess2, "precision_percept")

get_corplot(wb_fit_sess1, wb_fit_sess2, "alpha")
get_corplot(wb_fit_sess1, wb_fit_sess2, "w1")
get_corplot(wb_fit_sess1, wb_fit_sess2, "w2")
get_corplot(wb_fit_sess1, wb_fit_sess2, "beta")
get_corplot(wb_fit_sess1, wb_fit_sess2, "percept_precision")
